---
title: ''
author: "Catalyst California"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = FALSE, message = FALSE, warning = FALSE, echo = FALSE
)

library(sf)
library(highcharter)
library(rmapshaper)

options(highcharter.theme = hc_theme_smpl(tooltip = list(valueDecimals = 2)))
options(scipen=999)

source("W:\\RDA Team\\R\\credentials_source.R")
source("functions.R")

con <- connect_to_db("eci_mlaw")
con2 <- connect_to_db("rda_shared_data")

```

```{r load-data, include=FALSE}
# Read in postgres tables------------------------

# Read in LA city council districts shape
cd<-st_read(con2, query="SELECT * FROM geographies_la.lacitygeohub_lacity_council_districts_2023", geom="geom")%>%
  st_transform(4326)%>%
  ms_simplify()

index<-dbGetQuery(con, "SELECT * FROM pctiles_index")

# Read in la city zipcode xwalk
zip_xwalk<-st_read(con, query="SELECT * FROM crosswalk_zip_city_2022", geom="geom")%>%
  st_transform(4326)%>%
  ms_simplify()

# join index table with population data to the zip xwalk with our zip geoms
index<-zip_xwalk%>%
  left_join(index, by=c("zipcode"="geoid"))

```


## Domain Indices {.tabset .tabset-fade}
```{r domain-map-setup, include=FALSE}
# define color palettes for each domain
safe_env_pal <- c( "#FFBDA6" ,"#FF9873",  "#FA7B4D","#F25922","#DF4007")
econ_opp_pal <- c( "#E7AECD" ,"#C27AA1",  "#994E77","#733256","#601D42")
democracy_pal <- c( "#FFE4BB" ,"#FFD28F",  "#FFBC58","#FF9E0D","#EB8D00")
longevity_pal <- c( "#C9E3FF" ,"#9BCCFF",  "#5FABF9", "#177FEB","#0860BC")

nacolor <- "#9B9A9A"
```

### Safe Environments 

**What this domain means:** LA City residents experience safe environments with safety from pollution, traffic injuries, and harmful policing.

**What it includes:** Race Composite Score (Black, Latine, AIAN, NHPI, Asian); Particulate Matter (PM) 2.5; Proximity to Hazardous Waste Facilities; Pedestrian and Bicyclist Fatalities and Injuries; Arrests; Hospitalizations for Gun Injuries

```{r safe-environment-map}

# set pctile for mapping
df<-index%>%
  mutate(pctile=safe_environments_pctile)

# feed in indicator label for mapping popup and legend and group overlay
indicator<-paste0("Safe Environments")
direction<-paste0("higher")

# create popup: 
popup<- paste("<div class='leaflet-popup-scrolled' style='max-width:800px;max-height:200px'> <b>ZIP Code:</b> ", df$zipcode, "</br>",
"<b>","Safe Environments"," Percentile*: ", round(df$safe_environments_pctile,1),"</b></br>",
"<b>","Equity Index"," Percentile*:</b> ", round(df$index_pctile,1),"</br>",
 "<b>Population:</b> ", format(df$pop, big.mark=","), "</br></br>",
"<b>","Other Domain Percentiles:","</b></br>",
   "","Economy and Opportunity*: ", round(df$econ_opp_pctile,1),"</br>",
   "","Democracy and Power*: ", round(df$democracy_pctile,1),"</br>",
    "","Longevity and Vitality*: ", round(df$longevity_pctile,1),"</br>",
 "</br>",

"<i>*Percentiles range from 0-100. The higher the percentile, the ", direction," the need.</i>","</br>",
"</br></div>")

# map-----------------------------------
index_map(df=df, indicator=indicator, colorpalette=safe_env_pal, nacolor=nacolor, popup=popup)

```

### Economy and Opportunity

**What this domain means:** LA City residents have the opportunity to equitably engage in the economy.

**What it includes:** Race Composite Score (Black, Latine, AIAN, NHPI, Asian); Early Childhood Education (ECE) Enrollment; Rent Burden; Evictions; Per Capita Income

```{r econ-opp-map}

# set pctile for mapping
df<-index%>%
  mutate(pctile=econ_opp_pctile)

# feed in indicator label for mapping popup and legend and group overlay
indicator<-paste0("Economy and Opportunity")
direction<-paste0("higher")

# create popup: 
popup<- paste("<div class='leaflet-popup-scrolled' style='max-width:800px;max-height:200px'> <b>ZIP Code:</b> ", df$zipcode, "</br>",
"<b>","Economy and Opportunity"," Percentile*: ", round(df$econ_opp_pctile,1),"</b></br>",
"<b>","Equity Index"," Percentile*:</b> ", round(df$index_pctile,1),"</br>",
 "<b>Population:</b> ", format(df$pop, big.mark=","), "</br></br>",
"<b>","Other Domain Percentiles:","</b></br>",
   "","Safe Environments*: ", round(df$safe_environments_pctile,1),"</br>",
   "","Democracy and Power*: ", round(df$democracy_pctile,1),"</br>",
    "","Longevity and Vitality*: ", round(df$longevity_pctile,1),"</br>",
 "</br>",

"<i>*Percentiles range from 0-100. The higher the percentile, the ", direction," the need.</i>","</br>",
"</br></div>")

# map-----------------------------------
index_map(df=df, indicator=indicator, colorpalette=econ_opp_pal, nacolor=nacolor, popup=popup)

```

### Democracy and Power

**What this domain means:** LA City residents have the opportunity to equitably participate and influence democracy.

**What it includes:** Race Composite Score (Black, Latine, AIAN, NHPI, Asian); Limited English Speaking Households; Voter Turnout for the 2022 General Election

```{r democracy-map}

# set pctile for mapping
df<-index%>%
  mutate(pctile=democracy_pctile)

# feed in indicator label for mapping popup and legend and group overlay
indicator<-paste0("Democracy and Power")
direction<-paste0("higher")

# create popup: 
popup<- paste("<div class='leaflet-popup-scrolled' style='max-width:800px;max-height:200px'> <b>ZIP Code:</b> ", df$zipcode, "</br>",
"<b>","Democracy and Power"," Percentile*: ", round(df$democracy_pctile,1),"</b></br>",
"<b>","Equity Index"," Percentile*:</b> ", round(df$index_pctile,1),"</br>",
 "<b>Population:</b> ", format(df$pop, big.mark=","), "</br></br>",
"<b>","Other Domain Percentiles:","</b></br>",
   "","Safe Environments*: ", round(df$safe_environments_pctile,1),"</br>",
   "","Economy and Opportunity*: ", round(df$econ_opp_pctile,1),"</br>",
    "","Longevity and Vitality*: ", round(df$longevity_pctile,1),"</br>",
 "</br>",

"<i>*Percentiles range from 0-100. The higher the percentile, the ", direction," the need.</i>","</br>",
"</br></div>")

# map-----------------------------------
index_map(df=df, indicator=indicator, colorpalette=democracy_pal, nacolor=nacolor, popup=popup)

```

### Longevity and Vitality

**What this domain means:** LA City residents live with freedom from disease and illness and have the ability to access resources that increase community wellness.

**What it includes:** Race Composite Score (Black, Latine, AIAN, NHPI, Asian); Diabetes Hospitalizations; Impervious Land Cover; Health and Mental Health Care Services Access; Grocery Store Access

```{r longevity-map}

# set pctile for mapping
df<-index%>%
  mutate(pctile=longevity_pctile)

# feed in indicator label for mapping popup and legend and group overlay
indicator<-paste0("Longevity and Vitality")
direction<-paste0("higher")

# create popup: 
popup<- paste("<div class='leaflet-popup-scrolled' style='max-width:800px;max-height:200px'> <b>ZIP Code:</b> ", df$zipcode, "</br>",
"<b>","Longevity and Vitality"," Percentile*: ", round(df$longevity_pctile,1),"</b></br>",
"<b>","Equity Index"," Percentile*:</b> ", round(df$index_pctile,1),"</br>",
 "<b>Population:</b> ", format(df$pop, big.mark=","), "</br></br>",
"<b>","Other Domain Percentiles:","</b></br>",
   "","Safe Environments*: ", round(df$safe_environments_pctile,1),"</br>",
   "","Economy and Opportunity*: ", round(df$econ_opp_pctile,1),"</br>",
    "","Democracy and Power*: ", round(df$democracy_pctile,1),"</br>",
 "</br>",

"<i>*Percentiles range from 0-100. The higher the percentile, the ", direction," the need.</i>","</br>",
"</br></div>")

# map-----------------------------------
index_map(df=df, indicator=indicator, colorpalette=longevity_pal, nacolor=nacolor, popup=popup)

```



