---
title: ''
author: "Catalyst California"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = FALSE, message = FALSE, warning = FALSE, echo = FALSE
)

library(RPostgreSQL)
library(knitr)
library(dplyr)
library(sf)
library(leaflet)
library(htmltools)
library(stringr)
library(rgdal)
library(rpostgis)
library(leaflet)
library(RColorBrewer)
library(stringr)
library(scales)
library(colorspace)
library(highcharter) 
library(devtools)
library(rmapshaper)
# library(maptools)
library(rgeos)
# install.packages("corrplot")
library(corrplot)
# install.packages("Hmisc")
library(Hmisc)
options(highcharter.theme = hc_theme_smpl(tooltip = list(valueDecimals = 2)))
options(scipen=999)

source("W:\\RDA Team\\R\\credentials_source.R")

con <- connect_to_db("eci_mlaw")
con2 <- connect_to_db("rda_shared_data")

# Map function -------------------------

index_map<-function(df,indicator,direction,colorpalette,nacolor){
# add color palette for Indicator Percentiles

pctl.bins <-c(0, 20, 40, 60, 80, 100)

pal <- colorBin( palette = colorpalette, bins=pctl.bins, na.color = nacolor)

# create custom legend labels

labels <- c(
  "LOWEST NEED (0-19th Percentile)",
  "LOW NEED (20-39th Percentile)",
  "MODERATE NEED (40-59th Percentile)",
  "HIGH NEED (60-79th Percentile)",
"HIGHEST NEED (80-100th Percentile)"
)
# map

map<-leaflet(width = "100%", height = "600px")%>%
  
  # add base map
addProviderTiles("CartoDB.PositronNoLabels") %>%
addProviderTiles("CartoDB.PositronOnlyLabels", options = providerTileOptions(pane = "markerPane")) %>%

# add map panes
addMapPane("indi_pane", zIndex = 400) %>%
  addMapPane("cd_pane", zIndex = 400) %>%
  
  # set view and layer control
  setView( -118.353860, 34.068717, zoom = 9.5) %>%

  addLayersControl(overlayGroups = c(indicator, "City Council District"), 
                   options = layersControlOptions(collapsed = FALSE, autoZIndex = TRUE)) %>%
  
     # CD layer
addPolygons(data = cd, fillOpacity=0, color = '#CEEA01', weight = 2.2, label=~district, group = "City Council District", options = pathOptions(pane = "cd_pane", interactive = FALSE), highlight = highlightOptions(color = "white", weight = 3, bringToFront = TRUE))%>%
  
  # Indicator layer

  addPolygons(data=df, fillColor = ~pal(df$pctile), color="white", weight = 1, smoothFactor = 0.5, fillOpacity = .80, highlight = highlightOptions(color = "white", weight = 3, bringToFront = TRUE, sendToBack = TRUE), 
popup = ~popup,
group = indicator, options = pathOptions(pane = "indi_pane"))%>%
  
  # add legend
  
addLegend(position = "bottomleft", pal = pal, values = df$pctile, opacity = 1, title = paste0(indicator, " Percentile"), labFormat = function(type, cuts, p){paste0(labels)}) %>%
 hideGroup("City Council District")

map}


# Read in postgres tables------------------------

# Read in LA city council districts shape
cd<-st_read(con2, query="SELECT * FROM geographies_la.lacitygeohub_lacity_council_districts_2023", geom="geom")%>%
  st_transform(4326)%>%
  ms_simplify()

index<-dbGetQuery(con, "SELECT * FROM pctiles_index")

# Read in la city zipcode xwalk
zip_xwalk<-st_read(con, query="SELECT * FROM crosswalk_zip_city_2022", geom="geom")%>%
  st_transform(4326)%>%
  ms_simplify()

# join index table with population data to the zip xwalk with our zip geoms
index<-zip_xwalk%>%
  left_join(index, by=c("zipcode"="geoid"))

```


## Domain Indices {.tabset .tabset-fade}

### Safe Environments 

**What this domain means:** LA City residents experience safe environments with safety from pollution, traffic injuries, and harmful policing.

**What it includes:** Race Composite Score (Black, Latine, AIAN, NHPI, Asian); Particulate Matter (PM) 2.5; Proximity to Hazardous Waste Facilities; Pedestrian and Bicyclist Fatalities and Injuries; Arrests; Hospitalizations for Gun Injuries

```{r}

# set pctile for mapping

df<-index%>%
  mutate(pctile=safe_environments_pctile)

# feed in indicator label for mapping popup and legend and group overlay
indicator<-paste0("Safe Environments")
direction<-paste0("higher")

# feed in colorpalette
colorpalette <- c( "#E2D9FF" ,"#BDAFE9",  "#8E7ACA","#362178","#211447")
nacolor<-"#9B9A9A"

# pop up SEPARATE--------------------------

# create popup: 

popup<- paste("<div class='leaflet-popup-scrolled' style='max-width:800px;max-height:200px'> <b>ZIP Code:</b> ", df$zipcode, "</br>",
"<b>","Safe Environments"," Percentile*: ", round(df$safe_environments_pctile,1),"</b></br>",
"<b>","Equity Index"," Percentile*:</b> ", round(df$index_pctile,1),"</br>",
 "<b>Population:</b> ", format(df$pop, big.mark=","), "</br></br>",
"<b>","Other Domain Percentiles:","</b></br>",
   "","Economy and Opportunity*: ", round(df$econ_opp_pctile,1),"</br>",
   "","Democracy and Power*: ", round(df$democracy_pctile,1),"</br>",
    "","Longevity and Vitality*: ", round(df$longevity_pctile,1),"</br>",
 "</br>",

"<i>*Percentiles range from 0-100. The higher the percentile, the ", direction," the need.</i>","</br>",
"</br></div>")

# map-----------------------------------

index_map(df,indicator,direction,colorpalette,nacolor)

```

### Economy and Opportunity

**What this domain means:** LA City residents have the opportunity to equitably engage in the economy.

**What it includes:** Race Composite Score (Black, Latine, AIAN, NHPI, Asian); Early Childhood Education (ECE) Enrollment; Rent Burden; Evictions; Per Capita Income

```{r}

# set pctile for mapping

df<-index%>%
  mutate(pctile=econ_opp_pctile)

# feed in indicator label for mapping popup and legend and group overlay
indicator<-paste0("Economy and Opportunity")
direction<-paste0("higher")

# feed in colorpalette
colorpalette <- c( "#E2D9FF" ,"#BDAFE9",  "#8E7ACA","#362178","#211447")
nacolor<-"#9B9A9A"

# pop up SEPARATE--------------------------

# create popup: 

popup<- paste("<div class='leaflet-popup-scrolled' style='max-width:800px;max-height:200px'> <b>ZIP Code:</b> ", df$zipcode, "</br>",
"<b>","Economy and Opportunity Index"," Percentile*: ", round(df$econ_opp_pctile,1),"</b></br>",
"<b>","Equity Index"," Percentile*:</b> ", round(df$index_pctile,1),"</br></br>",
"<b>","Remaining Domain Indices:","</b></br></br>",
   "<b>","Safe Environments Index"," Percentile*:</b> ", round(df$safe_environments_pctile,1),"</br>",
   "<b>","Democracy and Power"," Percentile*:</b> ", round(df$democracy_pctile,1),"</br>",
    "<b>","Longevity and Vitality"," Percentile*:</b> ", round(df$longevity_pctile,1),"</br>",
 "<b>Population:</b> ", format(df$pop, big.mark=","), "</br>",
 "</br>",

"<i>*Percentiles range from 0-100. The higher the percentile score, the ", direction," the need.</i>","</br>",
"</br></div>")

# map-----------------------------------

index_map(df,indicator,direction,colorpalette,nacolor)

```

### Democracy and Power

**What this domain means:** LA City residents have the opportunity to equitably participate and influence democracy.

**What it includes:** Race Composite Score (Black, Latine, AIAN, NHPI, Asian); Limited English Speaking Households; Voter Turnout for the 2022 General Election

```{r}

# set pctile for mapping

df<-index%>%
  mutate(pctile=democracy_pctile)

# step 3: apply map function 

# feed in indicator label for mapping popup and legend and group overlay
indicator<-paste0("Democracy and Power")
direction<-paste0("higher")

# feed in colorpalette
colorpalette <- c( "#E2D9FF" ,"#BDAFE9",  "#8E7ACA","#362178","#211447")
nacolor<-"#9B9A9A"

# pop up SEPARATE--------------------------

# create popup: 

popup<- paste("<div class='leaflet-popup-scrolled' style='max-width:800px;max-height:200px'> <b>ZIP Code:</b> ", df$zipcode, "</br>",
"<b>","Democracy and Power"," Percentile*: ", round(df$democracy_pctile,1),"</b></br>",
"<b>","Equity Index"," Percentile*:</b> ", round(df$index_pctile,1),"</br></br>",
"<b>","Remaining Domain Indices:","</b></br></br>",
   "<b>","Safe Environments Index"," Percentile*:</b> ", round(df$safe_environments_pctile,1),"</br>",
   "<b>","Economy and Opportunity Index"," Percentile*:</b> ", round(df$econ_opp_pctile,1),"</br>",
    "<b>","Longevity and Vitality"," Percentile*:</b> ", round(df$longevity_pctile,1),"</br>",
 "<b>Population:</b> ", format(df$pop, big.mark=","), "</br>",
 "</br>",

"<i>*Percentiles range from 0-100. The higher the percentile score, the ", direction," the need.</i>","</br>",
"</br></div>")

# map-----------------------------------

index_map(df,indicator,direction,colorpalette,nacolor)

```

### Longevity and Vitality

**What this domain means:** LA City residents live with freedom from disease and illness and have the ability to access resources that increase community wellness.

**What it includes:** Race Composite Score (Black, Latine, AIAN, NHPI, Asian); Diabetes Hospitalizations; Impervious Land Cover; Health and Mental Health Care Services Access; Grocery Store Access

```{r}

# set pctile for mapping

df<-index%>%
  mutate(pctile=longevity_pctile)

# apply map function 

# feed in indicator label for mapping popup and legend and group overlay
indicator<-paste0("Longevity and Vitality")
direction<-paste0("higher")

# feed in colorpalette
colorpalette <- c( "#E2D9FF" ,"#BDAFE9",  "#8E7ACA","#362178","#211447")
nacolor<-"#9B9A9A"

# pop up SEPARATE--------------------------

# create popup: 

popup<- paste("<div class='leaflet-popup-scrolled' style='max-width:800px;max-height:200px'> <b>ZIP Code:</b> ", df$zipcode, "</br>",
"<b>","Longevity and Vitality"," Percentile*: ", round(df$longevity_pctile,1),"</b></br>",
"<b>","Equity Index"," Percentile*:</b> ", round(df$index_pctile,1),"</br></br>",
"<b>","Remaining Domain Indices:","</b></br></br>",
   "<b>","Safe Environments Index"," Percentile*:</b> ", round(df$safe_environments_pctile,1),"</br>",
   "<b>","Economy and Opportunity Index"," Percentile*:</b> ", round(df$econ_opp_pctile,1),"</br>",
    "<b>","Democracy and Power"," Percentile*:</b> ", round(df$democracy_pctile,1),"</br>",
 "<b>Population:</b> ", format(df$pop, big.mark=","), "</br>",
 "</br>",

"<i>*Percentiles range from 0-100. The higher the percentile score, the ", direction," the need.</i>","</br>",
"</br></div>")

# map-----------------------------------

index_map(df,indicator,direction,colorpalette,nacolor)


```



